To log or not to log

### 2022-07-21 main.tex
Updates from Overleaf

\documentclass{article}
\usepackage[]{graphicx}
\usepackage[]{xcolor}
\usepackage{alltt}
\usepackage[left=2.3cm,right=2.8cm, top = 2.2cm, bottom = 3cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage{url} 
\usepackage[disable]{todonotes}
\usepackage{multicol}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage[colorlinks=false]{hyperref} 
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%
\urlstyle{same}
\usepackage{lineno}
\linenumbers
\bibliographystyle{apalike}

@@

% to write the simulated as iid symbol: 
\newcommand{\distas}[1]{\mathbin{\overset{#1}{\kern\z@\sim}}}%

@@

Probabilistic forecasts play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as for example economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic and has been an important tool to inform public policy. Evaluating forecasts is important, as the evaluation provides feedback for forecasters and researchers necessary to improve their models, and it helps decision makers distinguish good from bad predictions and choosing forecasts that inform future decisions.

Proabbilistic forecasts are usually evaluated using so-called proper scoring rules, which return a numerical score as a function of the forecast and the later observed data. Forecasters, in expectaction, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. Two proper scoring rules commonly used in epidemiology and other fields are the Continuous Ranked Probability Score (CRPS) \citep{gneitingStrictlyProperScoring2007} and the Weighted Interval Score (WIS) \citep{bracherEvaluatingEpidemicForecasts2021}. Due to their widespread use in epidemiology we focus on these two in this paper, ignoring other proper scoring rules. Both the WIS and CRPS represent a measure of the absolute distance between the predictive distribution and observation and can be thought of as a generalisation of the absolute error to full predictive distributions (see details in the SI).

Evaluating forecasts based on absolute errors (for simplicity we use the term interchangeably with absolute distance, even though the former technically only applies to point forecasts) may not always be desirable, especially in an epidemiological context. 
% The reason for this is that generally, the way for ecasts are evaluated should correspond to the error structure of the model and the type of errors models will usually make.
Epidemiological processes are usually understood to be exponential in nature and therefore are most commonly described and modeled in multiplicative terms. Under the assumption that these models are correctly capturing the underlying inherent transmission dynamics, it would therefore make sense to focus evaluation on multiplicative, rather than absolute errors. Often, if the model is performing badly in multiplicative terms, this means that there is a flaw with its assumptions that needs to be resolved, regardless of performance in absolute terms. Evaluating epidemiological forecasts based on a measure of absolute error (as is common practice) can make it harder to diagnose and quantify model mis-specification. It also may make it more difficult to deal with the potential non-stationarity of epidemiological processes, or to compare performance across targets that are on very different orders of magnitudes (like for example cases and hospitalisations).

In this paper we argue that it may therefore be helpful to shift the focus of the evaluation on multiplicative, rather than absolute errors. This is approximately equal to scoring the growth rate of a forecast and can be achieved by transforming the forecasts as well as the observations using the logarithm before applying the WIS or CRPS. We focus on the log transformation, as it represents a very convenient way of achieving our goal of evaluating how well a forecast captures the growth dynamic inherent to epidemiological process. However, we note that the same logic we use can also applied to other transformations which could shift the focus of evaluation in different ways. For example, given an appropriate transformation, it could also be possible to evaluate forecasters based on the shape of the trajectory they predicted. It would even be possible to construct composite scores as a weighted sum of scores based on different transformations, allowing forecast consumers to assign explicit weights to different qualities of the forecasts.

In section [REF] we discuss the broader idea of transforming forecasts, and in section [REF] give a detailed theoretical of the log transformation and its interpretation. In section [REF] we present an applied example using forecasts submitted to the European COVID-19 Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. The European COVID-19 Forecast Hub is one of several Forecast hubs (together with a Hub in the US \citep{cramerEvaluationIndividualEnsemble2021} and one in Germany and Poland \citep{bracherShorttermForecastingCOVID192021} that systematically collected, aggregated and evaluated forecasts of several COVID-19 targets created by different teams. Forecasts submitted to the COVID-19 Forecast Hubs are probabilistic in nature [Citation e.g. Held et al.], meaning that forecasters provide a full predictive distribution which quantifies their uncertainty. These predictive distributions are reported in the form of a set of 23 quantiles (11 symmetric prediction intervals as well as a median prediction). 
%Currently, the US Flu Forecasting Hub and COVID-19 Scenario Hubs in the US and in Europe use the same format.

@@

Applying the log transformation, among other transformations, is permissible because it is a strictly monotonic transformation. While rankings between different models may indeed change, even for a single forecast, the relevant condition for a scoring rule to be strictly proper is still satisfied: In expectation a forecaster will receive the best score if she reports a predictive distribution that is equal to the data-generating distribution, even after transforming both the forecasts and the observations (representing draws from the data-generating distribution).

It is important to first apply the transformation and then score the transformed forecasts and observations. Simply taking the log of the WIS or the CRPS computed on the natural scale, i.e. computing $\log S(x, y)$ results in an improper score and is therefore not advised. This is because the logarithm of the WIS / CRPS does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/example-log-first.png}
    \caption{Scores for different forecasts evaluated the WIS and the log WIS. We simulated 1000 observations $Y_i = {\rm e}^{x_i}$, with $x_i \text{iid} \sim \mathcal{N}(0, 1)$. We then simulated 20 forecasters who would issue a predictive distribution $F = {\rm e}^{x_i}$, with $x \sim \mathcal{N}(0, \sigma)$, with values of $\sigma$ ranging from 0.1 to 2.}
    \label{fig:log-improper}
\end{figure}

\paragraph{Other transformations - maybe move to Discussion}
While we focus on the log transformation in this paper, there are other transformations that may be helpful in an epidemiological context. One could for example divide all forecasts by the population in a location, to obtain forecasts standardised incidences per e.g. 100,000 inhabitants. 
Or one could apply a Box-Cox transformation MISSING. 
Or a square-root transformation MISSING. 
Or one could divide each forecast by the forecast of the previous week (and observations by the observation of the previous week), to transform preditions to week-to-week growth rates. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory. Note that this is not well defined in the context of forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate.

% Divide by the latest known value = score forecast on the growth rate
% - WHAT KINDS OF DATA CAN I CONDITION ON? 
% - WOULD DIVIDING A FORECAST BY ITS RESOLUTION WORK? 
% - CAN I SCORE THE TRAJECTORY / WEEK-TO-WEEK GROWTH RATE BY DIVIDING the 4 week ahead forecast by the three week ahead forecast?

@@

% In this section (and those that follow) we focus on one particular transformation, taking the logarithm of forecasts and observations, which makes it possible to change the focus of the evaluation from absolute to relative errors. 
To illustrate the effects of applying the logarithm intuitively, let us consider a point forecast $\hat{y}_{t+1}$ for a quantity of interest $y_{t+1}$, such that 
\begin{equation}
y_{t+1} = \hat{y}_{t+1} + \varepsilon_{t+1}.
\end{equation}

The analogon of the WIS / CRPS for point forecasts is the absolute error, and so the score will be determined by the size of the forecast error $\varepsilon_{t+1}$. When taking the logarithm of the forecast and the observation first, then the score is determined based on the size of $\varepsilon^*_{t+1}$: 
\begin{equation}
\log y_{t+1} = \log \hat{y}_{t+1} + \varepsilon^*_{t+1}.
\end{equation}
%
It is easy to see that this corresponds to evaluating a multiplicative error on the original $y_{t+1}$:
%
\begin{align}
\log y_{t+1} &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \Leftrightarrow \\    
y_{t+1} &= \hat{y}_{t+1} \cdot \exp{\varepsilon^*_{t+1}}.    
\end{align}
%

On the natural scale, WIS and CRPS increase linearly with increasing absolute errors (see Figure \ref{fig:change-in-scores}A, regardless of whether the error is large in relative terms. Predicting 101,000 cases instead of the true 100,000 will be treated equally to predicting 2,000 hospitalisations, rather than the 1,000 observed. On the log scale, WIS and CRPS penalise relative errors and increase linearly with an increase in relative errors (see Figure \ref{fig:change-in-scores}D). Forecasting 101,000 rather than 100,000 cases will be treated equally to forecasting 2,020, rather than 2,000 hospitalisations. While the absolute error on the log scale is exactly symmetric (e.g., predicting 2 instead of 1 would give the same error as predicting 0.5), this is not entirely true for the WIS. Due to the fact that upper and lower bounds of individual prediction intervals are affected differently, there may be slight deviations (compare e.g. in Figure \ref{fig:change-in-scores}D the scores for a relative error of $\frac{1}{5}$ and 5).

@@

Now consider a forecast on $\log y_{t+1}$. Using the fact that for small values of $x$, $\log (1+ x) \approx x$, we can see that scoring forecasts on the log scale is approximately equal to scoring an additive error on the growth rate (on the natural scale), as long as the growth rate is small.
%
\begin{align}
\log y_{t+1}        &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \\
                    &= \log ((1 + \hat{g}_{t+1}) \cdot y_{t}) + \varepsilon^*_{t+1} \\
                    &= \log (1 + \hat{g}_{t, t+1}) + \log y_t + \varepsilon_{t+1} \Leftrightarrow \\
\varepsilon'_{t+1}  &= \log y_{t+1} -  \log y_t - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\    
                    &= \log (\frac{y_{t+1}}{y_t}) - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\    
                    &= \log (1 + g_{t, t+1}) - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\   
                    &\approx g_{t, t+1} - \hat{g}_{t, t+1} \quad \text{for small differences between} \hat{g}_{t, t+1} and g_{t, t+1}. 
\end{align}

This approximation breaks down when the difference between the predicted and the actual growth rate becomes too large (albeit forecasts are still evaluated in terms of relative errors). If this is of great concern one may want to use a different transformation like dividing forecasts and observations by the last known values instead in order to score the growth rate explicitly.

\subsection{Dealing with negative counts and small values}
Unfortunately, the log transformation cannot readily be applied when dealing with negative or zero values. In an epidemiological setting that involves count data, negative values should likely be omitted entirely. Values of zero should potentially also be removed from the analsys, as it does not make sense to interpret relative errors on zero counts. Alternatively, if one is not willing to omit them, a small quantity (such as 1) could be added to all observations before taking the logarithm. Note that predictive distribtions have to be truncated in a similar way. When dealing with count data we could extend this argument to all small values (rather than just zeros), as it is hard to reliably evaluate relative errors when dealing with small discrete values. One could therefore decide to remove forecasts for small quantities below a certain threshold from the analysis. Alternatively, one could add a number $n$ (e.g. $n = 100$) to all observations and forecasts before taking the logarithm. This also constitutes a strictly monotonic transformation which preserves propriety and would reduce all scores (through reducing relative errors). Scores for forecasts on small quantities would be particularly affected, resulting in a more equal distribution of scores for forecasts of differing orders of magntitudes. Researchers can choose to add either a small or large number, depending on how much they want to equalise relative errors when aggregating scores.

\subsection{Relative importance when summarising scores}
While the main rationale for applying the log transformation is that this better reflects the types of errors common in epidemiological modelling, it may also be helpful when scores based on the natural scale are very unequal. This usually happens, for example, when different forecast targets, like reported case numbers, hospitalisations and deaths, or the same targets across time and space, have very different orders of magnitude. In these instances, scores (even for an ideal forecaster) usually also differ by several orders of magnitude. Evaluating forecasts based on relative errors often makes it easier to compare performance across different targets more easily (as scores of an ideal forecaster would not differ as much as on the natural scale).

On the natural scale, aggregate scores will usually be dominated by predictions of quantities with high absolute values. The opposite may be true for scores based on log transformed predictions. Small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. The strength of this effect depends on the exact relationship between the mean and the variance of the quantity of interest. For simulated negative binomial count data, log predictions for small quantities receive on average higher scores than forecasts for large quantities if the mean and the variance grow at the same rate $\sigma^2 = \mu$, about equal scores when the variance grows at a rate of $\sigma^2 = \mu + \mu^2$ (Figure \ref{fig:SIM-wis-state-size-mean}), and smaller scores when the variance grows faster than that. 
%As mentioned above, one way to handle situations where scores are very unequal, is to add a number $n$ to all forecasts and observations in order to reduce the relative weight of forecast targets with small quantities.

@@

COULD ALSO BE DISCUSSION
Whether or not a log transformation is apprpriate depends on whether one believes that differences in absolute values are meaningful. This may be the case for example when comparing forecasts across locations or time points, rather than different forecasts targets. \cite{bracherEvaluatingEpidemicForecasts2021} for example argue that in epidemiological settings it is a desirable property of the CRPS / WIS that it assigns large scores to forecasts where counts are high, as this naturally reflects the situations we should most care about and helps us identify the models that perform best in similar situations. If, on the other hand, we believe that good models should do consistently well and that situations with high incidences do not provide significantly more information about which models perform well or badly, then scoring on the log scale may be more appropriate. For example, it may be reasonable not to think that predictive performance in a country like Germany would have a hundred times more importance than performance in a country like Luxembourg when determining the best model for future decision making. Similarly, we may not necessarily believe that predictive performance during the January 2022 wave of COVID-19 should carry three times as much weight than predictive performance during the January 2021 wave, just because numbers where three times as high. 
% Maybe make a plot with one country and scores for that one country in different waves. We could then argue that within one wave, performance of the peak is meaningful, but across different waves (with different numbers) it is unclear, whether that difference conveys meaningful information.

@@

%\begin{itemize}
%    \item Optional: Discussion of parallels to point forecasts and the point that you're still incentivised to report the median\\
%\end{itemize}

@@

\paragraph{Introduction to the Forecast Hub} As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Every week the European Forecast Hub collates and aggregates forecasts for different COVID-19 related targets from teams around the world. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$). The forecasts for the purpose of this illustrations are two-week-ahead forecasts made between XXX and XXX for reported cases and deaths from COVID-19 in XXX countries.

\paragraph{Describing features of the data}
Across all time points and locations, the mean number of cases (deaths) observed was 22811 (368) with an overall standard deviation of 47135 (831). The number of observed value does not only differ by forecast target, but also shows considerable heterogeneity by location (see Figure \ref{fig:HUB-mean-locations}. Across the different locations, the variance in observed values is roughly equal to the square of the mean, suggesting that, for a given location, both cases and deaths are not poisson-distributed, but rather exhibit over-dispersion. 
% MAYBE FIT A NEGATIVE BINOMIAL TO THESE OBSERVATIONS

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-mean-var-obs.png}
    \caption{Observed mean against observed variance of observations. The dashed line marks what would be expecetd from a negative binomially distributed variable with variance of the observed value equal to the mean + the square of mean observed value. }
    \label{fig:HUB-variance-mean}
\end{figure}

\paragraph{Features of the scores}
Across all time points and locations, the mean number weighted interval score on the natural scale for cases (deaths) was 8855 (59.3) with an overall standard deviation of 51274 (156). On the log scale, scores were much closer to each other (see Figure \ref{fig:HUB-average-scores}), with a mean WIS for cases (deaths) of 0.507 (0.362) with an overall standard deviation of 0.745 (0.407). 
% NEED A TABLE WITH SCORES for the Appendix
On the natural scale, scores vary by several orders of magnitudes across locations (see \ref{fig:HUB-scores-location}), whereas variation across locations is much smaller for scores on the log scale and wis values are more evenly distributed. The ordering of scores across locations is not preserved when going from the natural to the log scale (see Figure \ref{fig:HUB-mean-location}. Rather, there seems to be a slight inverse relationship that locations which previously had low scores now tend to receive higher scores. 
The correlation between scores on the log and natural scale for different locations is XX for cases and XX for deaths. 
BUT: CORRELATION FOR RANKINGS IS STILL LAGRGE

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-ranking-diffs.png}
    \caption{Distribution of rankings of the different Hub models. Rankings are computed as relative rankings, i.e. the ranking divided by the total number of models available for a given forecast target.}
    \label{fig:HUB-rankings}
\end{figure}

@@

@@

\paragraph{Rankings}
Rankings do change a little bit, but not massively. More difference comes when we look at greater forecast horizons.
Really this is more a point about how rankings change even for one single forecast (which I originally thought they shouldn't). Would be good to tease out what happens here. Somewhow we do change our judegement on which model is better. Maybe the preservation of the order really only holds for one interval? Or maybe not even that? 
Example: True value = 1
Forecaster 1: 0.8, 3.     Natural scale: 3.2 - 0.8 = 2.4.     Log scale: log 3 - log 0.8 = 1.386
Forecaster 2: 0.5, 2.8    Natural scale: 2.8 - 0.5 = 2.3    Log scale: log (2.8/0.5) = 1.722767
So one effect is that for a given dispersion on the natural scale, it's better if that interval is skewed, as that implies that at least you only off a lot in one direction in negative terms, and not in the other direction. Maybe looking at over-and underprediction is the key here. 
%ADD SAME PLOT TO SI FOR HORIZON 4.

\paragraph{pairwise comparisons}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-pairwise-comparisons.png}
    \caption{Changes in relative skill and the distribution of scores}
    \label{fig:HUB-pairwise}
\end{figure}

Correlation between pairwise comparisons is 0.4414717.

>>>>

\documentclass{article}
\usepackage[]{graphicx}
\usepackage[]{xcolor}
\usepackage{alltt}
\usepackage[left=2.3cm,right=2.8cm, top = 2.2cm, bottom = 3cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage{url} 
\usepackage[disable]{todonotes}
\usepackage{multicol}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage[colorlinks=false]{hyperref} 
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%
\urlstyle{same}
\usepackage{lineno}
\linenumbers

@@

@@

Probabilistic forecasts play an important role in decision-making in epidemiology and public health [Citations], as well as other areas as diverse as for example economics [Citations] or agriculture [Citations]. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic and has been an important tool to inform public policy. Evaluating forecasts is important, as the evaluation provides feedback for forecasters and researchers necessary to improve their models, and it helps decision makers with distinguishing good from bad predictions and choosing forecasts that inform future decisions.

Proabbilistic forecasts are usually evaluated using so-called proper scoring rules, which return a numerical score as a function of the forecast and the later observed data. Forecasters, in expectaction, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. Two proper scoring rules commonly used in epidemiology and other fields are the Continuous Ranked Probability Score (CRPS) [Gneiting 2007] and the Weighted Interval Score (WIS) [CITATION]. Due to their widespread use we focus on these two in this paper, ignoring other proper scoring rules. Both the WIS and CRPS represent a measure of the absolute distance between the predictive distribution and observation and can be thought of as a generalisation of the absolute error to full predictive distributions (see details in the SI).

Evaluating forecasts based on absolute errors (for simplicity we use the term interchangeably with absolute distance, even though it technically only applies to point forecasts) may not always be desirable, especially in an epidemiological context. 
% The reason for this is that generally, the way forecasts are evaluated should correspond to the error structure of the model and the type of errors models will usually make.
Epidemiological processes are usually understood to be exponential in nature and therefore are most commonly described and modeled in multiplicative terms. Under the assumption that these models are correctly capturing the underlying inherent transmission dynamics, it would therefore make sense to focus evaluation on multiplicative, rather than absolute errors. Often, if the model is performing badly in multiplicative terms, this means that there is a flaw with its assumptions that needs to be resolved, regardless of performance in absolute terms. Evaluating epidemiological forecasts based on a measure of absolute error (as is common practice) can make it harder to diagnose and quantify model mis-specification. It also may make it more difficult to deal with the potential non-stationarity of epidemiological processes, or to compare performance across targets that are on very different orders of magnitudes (like for example cases and hospitalisations).

In this paper we argue that it may therefore often be helpful to shift the focus of the evaluation on multiplicative, rather than absolute errors. This can be achieved by transforming the forecasts as well as the observations using the logarithm before applying the WIS or CRPS. While we will mostly focus on the log transformation in this paper, the point we like to make is a broader one: it is possible to flexible change the focus of the evaluation by applying a multitude of different transformations before scoring forecasts. Instead of scoring multiplicative errors, one may for example like to apply a transformation that allows to score forecasters based on the shape of the trajectory they predicted. Furthermore, it is possible to capture different aspects in a single number by constructing composite scores as a weighted sum of scores based on different transformations. This allows forecast consumers to assign explicit weights to different qualities of the forecasts they deem to be important when assessing predictive performance.

In section [REF] we discuss which kinds of transformations can be applied. In section [REF] we give a detailed theoretical explanation of the rationale for applying the log transformation and discuss its interpretation. In section [REF] we present an applied example using forecasts submitted to the European COVID-19 Forecast Hub. The European COVID-19 Forecast Hub is one of several Forecast hubs (together with a Hub in the US [CITATION] and one in Germany and Poland [CITATION]) that systematically collected, aggregated and evaluated forecasts of several COVID-19 targets created by different teams. Forecasts submitted to the COVID-19 Forecast Hubs are probabilistic in nature [Citation e.g. Held et al.], meaning that forecasters provide a full predictive distribution which quantifies their uncertainty. These predictive distributions are reported in the form of a set of 23 quantiles (11 symmetric prediction intervals as well as a median prediction). 
%Currently, the US Flu Forecasting Hub and COVID-19 Scenario Hubs in the US and in Europe use the same format.

@@

\subsection{Permissible transformations / propriety} - JOHANNES

In order to preserve the propriety of the score, transformations must be strictly monotonic. This makes sure that a forecast that is further away from the observed value will also be further away after the transformation.

- WHAT KINDS OF DATA CAN I CONDITION ON? 
- WOULD DIVIDING A FORECAST BY ITS RESOLUTION WORK? 
- CAN I SCORE THE TRAJECTORY / WEEK-TO-WEEK GROWTH RATE BY DIVIDING the 4 week ahead forecast by the three week ahead forecast? 
Probably does not work. 
Problem: Median von (X\_t+4 / X\_t+3) ist anders als Median

\paragraph{First transform, then score, rather than the other way round}
Note that simply taking the log of a score computed on the natural scale, i.e. computing $\log S(x, y)$ results in an improper score and is therefore not advised. We illustrate this point in Figure \ref{fig:log-improper} in the SI.

% \paragraph{Changes only come when you average across multiple scores}
% For a single forecast, the ranking between forecasters would be preserved and the scores remain proper [Proof?]. Differences in the ranking between forecasters only appear when averaging over multiple forecasts, as deviations from the perfect forecast get penalised differently depending on whether forecasts are transformed or not.

\paragraph{Example transformations}

Take the log

Divide by the latest known value = score forecast on the growth rate

Log that = score log growth rate

Divide by the previous for each time value, which gives you a weekly growth rate, i.e. a trajectory.

Box-Cox

square root WAS THAT USED SOMEWHERE? This is stabilising the variance. Kraus und Kraus. Idea: if X is poisson with some mean, then sqrt(x) has asymptotically a constant variance

Standardising by population size

@@

In this section (and those that follow) we focus on one particular transformation, taking the logarithm of forecasts and observations, which makes it possible to change the focus of the evaluation from absolute to relative errors. To illustrate the effects of applying the logarithm intuitively, let us consider a point forecast $\hat{y}_{t+1}$ for a quantity of interest $y_{t+1}$, such that 
\begin{equation}
y_{t+1} = \hat{y}_{t+1} + \varepsilon_{t+1}.
\end{equation}

The analogon of the WIS / CRPS for point forecasts is the absolute error, and so the score will be determined by the size of the forecast error $\varepsilon_{t+1}$. When taking the logarithm of the forecast and the observation first, than the score is determined based on the size of $\varepsilon^*_{t+1}$: 
\begin{equation}
\log y_{t+1} = \log \hat{y}_{t+1} + \varepsilon^*_{t+1}.
\end{equation}
%
It is easy to see that this corresponds to evaluating a multiplicative error on the original $y_{t+1}$:
%
\begin{align}
\log y_{t+1} &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \Leftrightarrow \\    
y_{t+1} &= \hat{y}_{t+1} \cdot \exp{\varepsilon^*_{t+1}}.    
\end{align}
%

On the natural scale, WIS and CRPS increase linearly with increasing absolute errors (see Figure \ref{fig:change-in-scores}A, regardless of whether the error is large in relative terms. Predicting 101,000 cases instead of the true 100,000 will be treated equally to predicting 2,000 hospitalisations, rather than the 1,000 observed. On the log scale, WIS and CRPS penalise relative errors and increase linearly with an increase in relative errors (see Figure \ref{fig:change-in-scores}D). Forecasting 101,000 rather than 100,000 cases will be treated equally to forecasting 2,020, rather than 2,000 hospitalisations. 
% Note that for a single forecast the relative rankings of different forecasts would be preserved. The transformation only makes a difference when aggregating predictions across different dimensions.

@@

Now consider a forecast on $\log y_{t+1}$. Using the fact that for small values of $x$, $\log (1+ x) \approx x$, we can see that scoring forecasts on the log scale is approximately equal to scoring an additive error on the growth rate (on the natural scale), as long as the growth rate is small.
%
\begin{align}
\log y_{t+1}        &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \\
                    &= \log ((1 + \hat{g}_{t+1}) \cdot y_{t}) + \varepsilon^*_{t+1} \\
                    &= \log (1 + \hat{g}_{t, t+1}) + \log y_t + \varepsilon_{t+1} \Leftrightarrow \\
\varepsilon'_{t+1}  &= \log y_{t+1} -  \log y_t - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\    
                    &= \log (\frac{y_{t+1}}{y_t}) - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\    
                    &= \log (1 + g_{t, t+1}) - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\   
                    &\approx g_{t, t+1} - \hat{g}_{t, t+1} \quad \text{for small } \hat{g}_{t, t+1}, g_{t, t+1}. 
\end{align}

%maybe it suffices that the difference between them is small. You can write them as a ratio and then the ratio just needs to be similar to one.

This approximation breaks down when the growth rate becomes too large. If scoring the growth rate is the focus of the evaluation, then it may be better to transform forecasts and observations by the last known values instead in order to score the growth rate explicitly.

\subsection{Dealing with negative counts and small values}
Unfortunately, the log transformation cannot readily be applied when dealing with negative or zero values. In an epidemiological setting that involves count data, negative values should likely be omitted entirely. Values of zero should potentially also be removed from the analsys, as it does not make sense to interpret relative errors on zero counts. Alternatively, if one is not willing to omit them, a small quantity (such as 1) could be added to all observations before taking the logarithm. Note that predictive distribtions have to be truncated in a similar way. When dealing with count data we could extend this argument to all small values (rather than just zeros), as it is hard to reliably evaluate relative errors when dealing with small discrete values. One could therefore decide to remove forecasts for small quantities below a certain threshold from the analysis. Alternatively, one could add a number $n$ (e.g. $n = 100$) to all observations and forecasts before taking the logarithm. This constitutes a strictly monotonic transformation which preserves propriety and would reduce all scores (through reducing relative errors). Scores for forecasts on small quantities would be particularly affected, resulting in a more equal distribution of scores for forecasts of differing orders of magntitudes. Researchers can choose to add either a small or large number, depending on how much they want to equalise relative errors when aggregating scores.

\subsection{Relative importance when summarising scores}
% Stationarity of forecast timelines

For a single transformation, the ranking between models is preserved, even though the numeric value of the score changes. However, when averaging across forecasts, the relative influence of individual forecasts on the aggregate score may differ dramatically, leading to changes in the overall model rankings. While the main rationale for applying the log transformation is that this better reflects the types of errors common in epidemiological modelling, it may also be helpful when scores based on the natural scale are very unequal. This usually happens, for example, when different forecast targets, like reported case numbers, hospitalisations and deaths, or the same targets across time and space, have very different orders of magnitude. In these instances, scores (even for an ideal forecaster) usually also differ by several orders of magnitude. Evaluating forecasts based on relative errors often makes it easier to compare performance across different targets more easily (as scores of an ideal forecaster would not differ as much as on the natural scale).

While on the natural scale, aggregate scores will usually be dominated by predictions of quantities with high absolute values, the opposite may be true for scores based on log transformed predictions. Small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. The strength of this effect depends on the exact relationship between the mean and the variance of the quantity of interest. For simulated negative binomial count data, log predictions for small quantities receive on average higher scores than forecasts for large quantities if the mean and the variance grow at the same rate $\sigma^2 = \mu$, about equal scores when the variance grows at a rate of $\sigma^2 = \mu + \mu^2$ (Figure \ref{fig:SIM-wis-state-size-mean}), and smaller scores when the variance grows faster than that. As mentioned above, one way to handle situations where scores are very unequal, is to add a number $n$ to all forecasts and observations in order to reduce the relative weight of forecast targets with small quantities.

@@

COULD ALSO BE DISCUSSION
Whether or not a log transformation is apprpriate depends on whether one believes that differences in absolute values are meaningful. This may be the case for example when comparing forecasts across locations or time points, rather than different forecasts targets. \citep{Bracher} for example argue that in epidemiological settings it is a desirable property of the CRPS / WIS that it assigns large scores to forecasts where counts are high, as this naturally reflects the situations we should most care about and helps us identify the models that perform best in similar situations. If, on the other hand, we believe that good models should do consistently well and that situations with high incidences do not provide significantly more information about which models perform well or badly, then scoring on the log scale may be more appropriate. For example, it may be reasonable not to think that predictive performance in a country like Germany would have a hundred times more importance than performance in a country like Luxembourg when determining the best model for future decision making. Similarly, we may not necessarily believe that predictive performance during the January 2022 wave of COVID-19 should carry three times as much weight than predictive performance during the January 2021 wave, just because numbers where three times as high. 
% Maybe make a plot with one country and scores for that one country in different waves. We could then argue that within one wave, performance of the peak is meaningful, but across different waves (with different numbers) it is unclear, whether that difference conveys meaningful information.

@@

%COMPARISON TO SCORING THE ACTUAL GROWTH RATE - just harder to do and achieves the same thing? No objections if someone wants to? Might actually be better if there are negative values involved?

%What about other things like scoring the square root of the forecast?

%\begin{itemize}
%    \item discuss how equations change for CRPS
%    \item Optional: Discussion of parallels to point forecasts and the point that you're still incentivised to report the median\\
%    \item discuss that even if both scoring rules are proper, they still penalise different things %differently. How does that change incentives for the forecaster? 
%\end{itemize}

\paragraph{Toy example: simulate an epidemic and apply 3 different models} Compare scores for these three models on the natural scale and the log scale

@@

\paragraph{Introduction to the Forecast Hub} As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021}. Every week the European Forecast Hub collates and aggregates forecasts for different COVID-19 related targets from teams around the world. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$). The forecasts for the purpose of this illustrations are two-week-ahead forecasts made between XXX and XXX for reported cases and deaths from COVID-19 in XXX countries.

\paragraph{Describing features of the data}
Across all time points and locations, the mean number of cases (deaths) observed was 22811 (368) with an overall standard deviation of 47135 (831). The number of observed value does not only differ by forecast target, but also shows considerable heterogeneity by location (see Figure \ref{fig:HUB-mean-locations}. Across the different locations, the variance in observed values is roughly equal to the square of the mean, suggesting that, for a given location, both cases and deaths are not poisson-distributed, but rather exhibit over-dispersion. 
MAYBE FIT A NEGATIVE BINOMIAL TO THESE OBSERVATIONS

@@

\paragraph{Features of the scores}
Across all time points and locations, the mean number weighted interval score on the natural scale for cases (deaths) was 8855 (59.3) with an overall standard deviation of 51274 (156). On the log scale, scores were much closer to each other (see Figure \ref{fig:HUB-average-scores}), with a mean WIS for cases (deaths) of 0.507 (0.362) with an overall standard deviation of 0.745 (0.407). 
% NEED A TABLE WITH SCORES for the Appendix
On the natural scale, scores vary by several orders of magnitudes across locations (see \ref{fig:HUB-scores-location}), whereas variation across locations is much smaller for scores on the log scale and wis values are more evenly distributed. The ordering of scores across locations is not preserved when going from the natural to the log scale. 
% Rather, there seems to be a slight inverse relationship that locations which previously had low scores now tend to receive higher scores. 
The correlation between scores on the log and natural scale for different locations is XX for cases and XX for deaths. 
%THERE SEEMS TO BE A TENDENCY FOR SMALLER

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-scores-locations.png}
    \caption{Weighted interval scores across different locations for two week ahead forecasts of COVID-19 cases and deaths evaluated on the natural scale (left) and on the log scale (right). }
    \label{fig:HUB-scores-location}
\end{figure}
% Could also sort this figure according to population size?
%Make multi panel Figure with Figure 2 and sort according to mean outcome

@@
